Approximating the Optimal State Abstraction

### 2016-05-01 icml_workshop/framework.tex
A merge and stuff

\section{Abstraction Framework}

In previous work~\cite{abelhershko2016approx}, we extended the unifying framework of state abstraction proposed by~\cite{li2006towards}. We developed a theory of approximate abstraction, in which abstraction is interpreted as state aggregation; that is, a state abstraction function $\phi : \mathcal{S}_G \mapsto \mathcal{S}_A$, induces a full abstract \ac{MDP} according to the methods described by~\cite{li2006towards}.

@@

This theorem satisfies the \textsc{Value} desiderata. Moreover, we stipulate that functions of these classes are learnable due to the criteria of $\varepsilon$-closeness, as was demonstrated by~\cite{ortner2007logarithmic}. Furthermore, we empirically demonstrate the compressibility of these functions, and consider it an open problem as to what degree of compressibility is achievable under this framework.

>>>>

\section{Abstraction Framework}
\cite{li2006towards} previously provided a unifying treatment of state aggregation functions. In this work a state abstraction function produces an abstract \ac{MDP}, $M$ from a ground \ac{MDP}, $M_G$ b $\phi : \mathcal{S}_G \mapsto \mathcal{S}_A$, induces a full abstract \ac{MDP} $M)A$ DO THIS BETTER

 \cite{li2006towards} provides sufficient conditions on a state aggregation function, $\phi : \mathcal{S}_G \mapsto \mathcal{S}_A$ to fully maintain optimality. Thus, \cite{li2006towards} provides sufficient conditions whereby \textsc{Optimality} and (hopefully but not provably) \textsc{Compressability} are satisfied. However, the criteria proposed by \cite{li2006towards} are no more difficult than solving the ground \ac{MDP} and so this work fails to satisfy \textsc{Efficient-Computability}. In hopes to provide a notion that satisfies \textsc{Efficient-Computability} we provided an $\epsilon$-relaxation of the conditions proposed in \cite{li2006towards}.

 provides a number of sufficient conditions whereby optimality in the abstract \ac{MDP} is fully maintained when the abstract \ac{MDP} is generated by a state aggregation function, $\phi : \mathcal{S}_G \mapsto \mathcal{S}_A$ which reduced of an

provided a number of sufficient conditions under which However, . understands an abstraction as a state abstraction function $\phi : \mathcal{S}_G \mapsto \mathcal{S}_A$

We developed a theory of approximate abstraction, in which abstraction is interpreted as state aggregation; that is, a state abstraction function $\phi : \mathcal{S}_G \mapsto \mathcal{S}_A$, induces a full abstract \ac{MDP} according to the methods described by~\cite{li2006towards}.

@@

This theorem satisfies the \textsc{Value} desiderata. Moreover, we suspect that functions of these classes are learnable due to the criteria of $\varepsilon$-closeness, as was demonstrated by~\cite{ortner2007logarithmic}. Furthermore, we empirically demonstrate the compressibility of these functions, and consider it an open problem as to what degree of compressibility is provably achievable under this framework.
